{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-03-06 documents/charge.tex
words
Text and prop improvements
More progress on summary
More details

\section{Charge}

@@

The adsorption of metal ions onto the surface of the genome
\begin{itemize}
\item The nucleocapsid. 
\item Induced polarization
		Persson cite a polarization re-arrangement of electrons as a source of drag. Polarization-like effects are not expected. We have not followed up on this.
\item 
\end{itemize}

@@

Donnan equilibrium

@@

At the largest scale, at a pH of 7 the net charges of the 4 proteins that comprise ~88\% of the protein mass\cite{Quantitative1981} of the virus (of the 11 coded for by the Influenza A genome) only contribute at most  $\approx 1 \times 10^5\  e^-$.

>>>>

\clearpage
\section{Charge}

@@

The adsorption of metal ions onto the surface of the genome
\begin{itemize}
\item The nucleocapsid. 
\item Induced polarization
		Persson cite a polarization re-arrangement of electrons as a source of drag. Polarization-like effects are not expected. We have not followed up on this.
\item Donnan equilibrium
\end{itemize}

@@

@@

At the largest scale, at a pH of 7, the net charges of the 4 proteins that comprise ~88\% of the protein mass\cite{Quantitative1981} of the virus (of the 11 coded for by the Influenza A genome) only contribute at most  $\approx 1 \times 10^5\  e^-$.

### 2021-03-06 documents/experiment_1_data.tex
More details

		\hline
		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses 84.8 V/m pessimistic to 339 V/m optimistic} \\
		\hline
		Sham   & 12 & Run 8 t4,5...\\
		+ & 11 & Run 8 t4,5...\\
		+  & 12 & Run 8 t4,5...\\
		+  & 12 & Run 8 t4,5...\\
		\hline
		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, phage degraded with basic buffer, 84.8 V/m pessimistic to 339 V/m optimistic} \\
		\hline
		Blank (0 min) & 14 & Run 9 \\
		Blank (\ntilde 15 min) & 17 & Run 9\\
		Sham (\ntilde 15 min) & 5 & Run 9\\
		Blank (\ntilde 4 hr) & 24 & Run 9\\
		\hline
		+  & 14 & Run 11\\
		Sham & 17 & Run 11\\
		\hline
		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses, 84.8 V/m pessimistic to 339 V/m optimistic} \\
		\hline
		Sham & 12 & Run 12\\
		+    & 10 & Run 12\\
		\hline
		\multicolumn{3}{|c|}{\textbf{0.2 mm channel}, 6 to 12 GHz, 10 or 20 us CW pulses, 200 V/m pes. and 10.6 kV/m opt.} \\
		\hline
		 Sham & 12 & CPWG micro-\\
 		 +    & 10 & CPWG micro-\\

@@

 		\hline
		\multicolumn{3}{|c|}{\ntilde 0.2 mm channel, various pulse counts and termination, 0.155 MV/m to 5.6 MV/m} \\
		\hline 
		 Blank    & 8 & Li test 1\\
		 +           & 8 & Li test 1\\
 		 +           & 7 & Li test 1\\
 		 +           & 7 & Li test 1\\
 		 + \& shaper & 7 & Li test 1\\
 		 \hline

		\multicolumn{3}{|c|}{\ntilde 0.03 mm channel, 0.2 uL/s, various pulse counts and termination, 1 MV/m to 38 MV/m} \\
		\hline
		Sham & 5 & Smaller \\
		+ & 6 & Smaller \\ 
		+ & 6 & Smaller  \\ 
		\hline

		\multicolumn{3}{|c|}{\ntilde 0.03 mm channel, basic buffer, tainted as pH may not have been 10.6, 1 MV/m to 38 MV/m} \\
		\hline
		Sham & 12 & Weakened \\ 
		Blank & 11 & Weakened  \\ 
		Blank & 12 & Weakened  \\ 
		Blank & 9 & Weakened  \\ 
		+ & 11 & Weakened \\
		+ (no term) & 11 & Weakened \\ 
		+ & 9 & Weakened \\ 
		\hline
	\end{tabular}
\end{table}

Original notes for this table can be inspected at \ghfile{firmware/eppenwolf/pulse_1.pnw}. Data rounded to the nearest thousand fluorescence photon counts per 10 seconds. Larger numbers are presumed to correlate with greater capsid damage.

See notes on experiment design and data collection in main body.

>>>>

		\hline
		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses, 85 V/m to 339 V/m expected} \\
		\hline
		Sham   & 12 & Run 8 t4,5...\\
		+ & 11 & Run 8 t4,5...\\
		+  & 12 & Run 8 t4,5...\\
		+  & 12 & Run 8 t4,5...\\
		\hline
		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, phage degraded with basic buffer, 85 V/m to 339 V/m expected} \\
		\hline
		Blank (0 min) & 14 & Run 9 \\
		Blank (\ntilde 15 min) & 17 & Run 9\\
		Sham (\ntilde 15 min) & 5 & Run 9\\
		Blank (\ntilde 4 hr) & 24 & Run 9\\
		\hline
		+  & 14 & Run 11\\
		Sham & 17 & Run 11\\
		\hline
		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses} \\
		\hline
		Sham & 12 & Run 12\\
		+    & 10 & Run 12\\
		\hline
		\multicolumn{3}{|c|}{\textbf{0.2 mm channel}, 6 to 12 GHz, 10 or 20 us CW pulses, 200 V/m to 850 V/m exp., 10.6 kV/m pk} \\
		\hline
		 Sham & 12 & CPWG micro-\\
 		 +    & 10 & CPWG micro-\\

@@

 		\hline
		\multicolumn{3}{|c|}{\ntilde 0.2 mm channel, various pulse counts and termination, 0.155 MV/m expected, 5.6 MV/m peak} \\
		\hline 
		 Blank    & 8 & Li test 1\\
		 +           & 8 & Li test 1\\
 		 +           & 7 & Li test 1\\
 		 +           & 7 & Li test 1\\
 		 + \& shaper & 7 & Li test 1\\
 		 \hline

		\multicolumn{3}{|c|}{\ntilde 0.03 mm channel, 0.2 uL/s, various pulse counts and termination, 1 MV/m expected, 38 MV/m peak} \\
		\hline
		Sham & 5 & Smaller \\
		+ & 6 & Smaller \\ 
		+ & 6 & Smaller  \\ 
		\hline

		\multicolumn{3}{|c|}{\ntilde 0.03 mm channel, basic buffer, tainted as pH may not have been 10.6, 1 MV/m exp., 38 MV/m pk} \\
		\hline
		Sham & 12 & Weakened \\  
		Blank & 11 & Weakened  \\ 
		Blank & 12 & Weakened  \\ 
		Blank & 9 & Weakened  \\ 
		+ & 11 & Weakened \\
		+ (no term) & 11 & Weakened \\ 
		+ & 9 & Weakened \\ 
		\hline
	\end{tabular}
\end{table}
%how many pulses?

Original notes for this table can be inspected at \ghfile{firmware/eppenwolf/pulse_1.pnw}. Data rounded to the nearest thousand fluorescence photon counts per 10 seconds. Larger numbers are presumed to correlate with greater capsid damage (see Autoclaved).

Note the width of the electric field bounds. These are not meaningful random or systematic intervals; we can only confidently assert that the field did not exceed the peak value at any point within the channel. Expected values based on FDTD simulation and voltage; peak based on channel width and voltage.

See notes on experiment design and data collection in main body and GitHub supplemental.

### 2021-03-06 documents/summary.tex
More details

	\caption*{\small{\textit{Chengxiang} nanosecond pulse exposure jig. Aluminum disc belongs to the scan-conversion digitizer, not used in this study.}}
		\caption*{\small{Pulsed X-Band microwave spectrometer used in this study.}}
				\caption*{\small{FDTD simulation geometry of the 0.2 mm coplanar waveguide exposure cell. }}
						\caption*{\small{The very pretty opalescent blue culture caused by E. coli B and X-gal.}}
						\caption*{\small{Fluorescence reader used.}} 
%	\caption{Brillouin precursor propagation through tissue (reproduced from section 6).\\
%		(a) Gaussian monopulse with 16 ps FWHM.\\
%		(b) Optimized 10 GHz sawtooth wave. Note the slight high-frequency ripple.\\ This has a frequency of approximately 1.5 GHz.\\
%		(c) Prototypical precursor 10 GHz sine burst.\\
%		(d) Continuous 10 GHz sine tone.}
\end{figure}
\clearpage

@@

We have some minor questions regarding experimental technique in the original papers that can only be addressed by more extensive replication studies, and luckily are due to be answered by other groups\cite{Generating}, so we try not to defer greatly to their observations.

These studies are all founded on the idea that some large-scale structural difference between viruses and all host cellular structures might usable as leverage to selectively inactivate the virus by some physical - rather than biological - means. For example, such an inactivation "window" between host cell and virion damage has been found in certain wavelengths of CW Far UV\cite{Germicidal2017} - but also apparently in certain modulated UV pulses\cite{Use1987a}\cite{Can1993}, and also sporadically reported for simple thermal treatment\cite{Summary}; however, the differential inactivation modes found so far do not appear to be of much use in the clinic.

A few well-established non-resonant non-thermal effects caused by extreme electric fields have already been put to practical use. Electroporation\cite{Electroporation1988} is a common laboratory procedure in which an enormous electric field causes ions in solution to diffuse across a host cell's membrane, capacitively charging it. This leads to a change in lipid conformation, reversibly rendering the membrane permeable (among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's understanding\cite{Theoretical2007}).

@@

Compare to $~5 k_b T$ per protein for 1 capsid segment binding energy \cite{Energies2012} \cite{Weak2002} and 6 to 30 $k_b T$ to form a single pore in a lipid bilayer \cite{Atomistic2014}. \cite{Electrostatic2020a}
%17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT

Brackley \cite{Electrostatic2020} describe various analytic representations of the charge screening about the virion with the Poisson-Boltzmann equation.

From a force perspective, the $10^3$ genome charge easily provides the nanonewton force scale required\cite{Bacteriophage2004} to break capsids or envelopes in 5 MV/m fields; but accurate estimation of the capsid stress will require application of the Maxwell stress tensor \cite{Electrostatic2013}\cite{Deformation1991}

On the other hand, such a sub-angstrom movement can only induce approx. 0.05\% deflection of the capsid, whereas a general value for the rupture of host cells is about 3\% deflection\cite{Electromechanical1989}. The stiffness of the genome could be used to explain this. With a relaxation time on the order of 500 ps, it is difficult to imagine that this energy will be sufficiently concentrated in the capsid to be destructive. After the relaxation time, only the mechanical effects that were induced can remain.

Modelling this sort of multi-scale inactivation mechanism involving the collective motion of some $10^9$ atoms poses a significant computational and theoretical hassle, which has far exceeded our capabilities.

Coarse-graining; but, as with all simulations, the problem must be set up with great care and experience (polarizable water; proper heat-bath damping coefficients and choice of integrator)\cite{Membrane2016}, and with an understanding of possible failure modes; we did not trust our abilities to produce correct results. Parametrizing based on all-atom simulations of small capsid segments or proteins \cite{Elucidating2009}. Mechanically reasonable coarse-grained models have recently been published for SARS-NCoV-2\cite{Multiscale2020}. DNA can be represented by homogeneous beads restrained by Lennard-Jones forces \cite{Communication2013}. Finite-element analysis \cite{Finite2008}

Coupling FEM \cite{Electrostatic2020a}.

Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition - or even perhaps directly, via extraction from whole-virion CryoEM maps, because of the charge-sensitive nature of the technique \cite{Identification2018}\cite{Electrostatic2020}. This has not yet been implemented in any software tools and seems quite tricky. The genome charge is almost entirely neutralized by the nucleocapsid.

GROMACS simulations of liposomes, trajectories fourier transformed with \cite{TRAVIS2011}.

In our cursory testing, Bacteriophage T4 did not appear to be lysed by 10 microsecond pulses between 6 and 12 GHz at about 70 V/m, nor, exploring non-resonant inactivation, did nanosecond pulses up to 1 MV/m appear to have any effect. Note that neither of these regimes overlap with the results of the previous studies.

@@

A rotational drag coefficient can extracted from MD simulation\cite{Evaluating2017}. We simulated a 30 nm lipid liposome using the MARTINI coarse-grained \cite{MARTINI2007} lipid force fields with GROMACS\cite{GROMACS2005}' torque measurement feature, kindly implemented by Kutzner \cite{Keep2011}. This suggests a maximum rotation frequency at on the order of $10^3$, but this value requires so many assumptions that it's hardly worth mentioning. From \cite{Spinning2008}, the upper bound of a homogenous spherical virus with 10 MPa overall tensile strength appears to be about $10^9$ Hz. \footnote{\ghfile{documents/optical_centrifuge.ipynb}}

@@

Dispersion and Brillouin precursors do offer a significant improvement in loss through tissue, and the required electrical waveforms appear to be synthesizeable by variable-impedance or stub transmission-line pulse shaping\cite{Coaxial1985}\cite{Arbitrarya}.

@@

T4 was selected for biosafety reasons, and because of the large amount of structural data available. T4 does not have a nucleocapsid; the charge distribution is likely much stronger than other RNA-like viruses Phi 6\footnote{Naming organisms with greek letters makes literature review somewhat more difficult, because many search engines do not support Unicode.}. Some more useful surrogates may include Pseudomonas Phi 6\cite{Selection2017}, the lipid-bearing PM2, PRD1 or PR4\cite{Lipidcontaining1979} if the outer protein capsid is dissolved\cite{Bacteriophage2002}, \cite{Dissociation1993}, or lipid liposomes. Certain phages also allow efficient concentration without ultracentrifuge, either by PEG precipitation\cite{Rapid1970} and settling, or via VIRADEL\cite{GROWTH}\cite{Chemical1982}\cite{highly1988}\cite{AdsorptionElution1989}, by altering the zeta potential of a syringe filter.

@@

30 atmospheres. When phage is rapidly immersed in solution of high osmotic strength, the active system that maintains osmotic equilibrium is overwhelmed, and the resulting force ruptures the capsid. \cite{Osmotic2003}, and breaks at a pressure differential of 100 atm. By $\sigma = pr / 2t $ t = 5.7 nm\cite{Head1988} and r=60 nm, capsid strength should be about 53 MPa, less than the 100 to 300 MPa cited by \cite{Bacteriophage2004}.
%((100 atm * 60 nanometers) / (2*(5.7 nanometers))) to MPa

@@

E. coli produces the enzyme $\beta$-galactosidase to break lactose into glucose for later metabolism. A luciferase-based luminescent assay, Promega Beta-Glo, was evaluated. One component of the beta-glo contains a proprietary detergent designed to lyse cells\cite{BETAGLO2003} and expose the enzyme, counterproductive for phage use. Perhaps the detergent is not effective on bacteria, or the paper substrate that w\cite{rapid2014}as used is sufficient. The detergent could perhaps be removed with BioBeads if this is desired.

While undoubtedly essential and very effective for its intended purpose (accurately quantifying lac operon activity), because of ambiguities in the rise and decay of the luminescence signal, short shelf life after the two components are mixed, oxygen depletion in small cuvettes, concerns regarding the detergent, and cost, Beta-Glo compared unfavorably to direct fluorescence or X-Gal for this application.

@@

\subsection{Notes}

@@

\section{Discussion}

>>>>

	\caption*{\small{\\
	(a) \textit{Chengxiang} nanosecond pulse exposure jig. Aluminum disc belongs to the scan-conversion digitizer, not used in this study.\\
	(b) Pulsed X-Band microwave spectrometer used.\\
	(c) Simulation of a (largely ineffective) bronchoscopic method.\\
	(d) FDTD simulation geometry of the 0.2 mm coplanar waveguide exposure cell.\\
	(e)	The very pretty opalescent blue culture caused by E. coli B uptake of X-Gal.\\
	(f) Fluorescence reader used.\\
}}
%		\caption*{\small{}}
%				\caption*{\small{FDTD simulation geometry of the 0.2 mm coplanar waveguide exposure cell. }}
%						\caption*{\small{The very pretty opalescent blue culture caused by E. coli B and X-gal.}}
%						\caption*{\small{Fluorescence reader used.}} 
%	\caption{Brillouin precursor propagation through tissue (reproduced from section 6).\\
%		(a) Gaussian monopulse with 16 ps FWHM.\\
%		(b) Optimized 10 GHz sawtooth wave. Note the slight high-frequency ripple.\\ This has a frequency of approximately 1.5 GHz.\\
%		(c) Prototypical precursor 10 GHz sine burst.\\
%		(d) Continuous 10 GHz sine tone.}
\end{figure}
\clearpage

@@

%We have some minor reservations regarding experimental technique in the original papers that can only be addressed by more extensive replication studies, and luckily are due to be answered by other groups\cite{Generating}, so we try not to defer greatly to their observations.

These studies are all founded on the idea that some large-scale structural difference between viruses and all host cellular structures might usable as leverage to selectively inactivate the virus by some physical - rather than biological - means. For example, such an inactivation "window" between host cell and virion damage has been found in certain wavelengths of CW Far UV\cite{Germicidal2017} - but also apparently in certain modulated UV pulses\cite{Use1987a}\cite{Can1993}, and also sporadically reported for simple thermal treatment\cite{Summary}; however, the modes exhibiting differential inactivation that have been found so far do not appear to be of particular use in the clinic.

Some possible minor shortcomings of the original experiments are due to be addressed by other groups\cite{Generating}, so we try not to defer greatly to those observations.

A few well-established non-resonant non-thermal effects caused by extreme electric fields have already been put to practical use. Electroporation\cite{Electroporation1988}, now a common laboratory procedure, occurs when an enormous electric field causes ions in solution to diffuse across a cell membrane, capacitively charging it. This leads to a change in lipid conformation, reversibly rendering the membrane permeable (among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's understanding\cite{Theoretical2007}).

@@

Compare to $~5 k_b T$ per protein for 1 capsid segment binding energy \cite{Energies2012} \cite{Weak2002} and 6 to 30 $k_b T$ to form a single pore in a lipid bilayer \cite{Atomistic2014}. 
%17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT

With a relaxation time on the order of 500 ps, it is somewhat difficult to imagine that this energy will be sufficiently concentrated in the capsid to be destructive. After the relaxation time, only the mechanical effects that were induced can remain, unless some progressive chemical or fatigue-like degradation occurs.

Brackley \cite{Electrostatic2020} describe various analytic representations of the charge screening about the virion with the Poisson-Boltzmann equation; by translating the obtained charge into a steady-state Poisson simulation (ions will not migrate in nanosecond pulse timescales), a relatively representative simulation may be obtained\footnote{implementation attempted at \ghfile{/math/mathematica/analytic_force.nb}}.

\end{multicols}
\begin{autem}
	autem, discuss\\
	At the risk of seeming a fool, what is the correct metric for the charge quantity being discussed? We are interested in the stress produced by a certain arbitrary distribution of charge. Assuming a spherically symmetric virus composed of two charged shells, there is no intrinsic dipole moment. Polarizability or induced dipole moment are not obviously relevant; stress could be produced in an extremely stiff structure with no electron mobility. The virion has little net charge. Multipole expansions are not clearly relevant.
\end{autem}
\begin{multicols}{1}
From a force perspective, the $10^3$ genome charge easily provides the nanonewton force scale required\cite{Bacteriophage2004} to break capsids or envelopes in 5 MV/m fields; but accurate estimation of the capsid stress will likely require application of the Maxwell stress tensor \cite{Electrostatic2013}\cite{Deformation1991}.

On the other hand, such a sub-angstrom movement can only induce approximately a 0.05\% deflection of the capsid, whereas a general value for the rupture of host cells is about 3\% deflection\cite{Electromechanical1989}. The stiffness of the genome could be used to explain this.

Accurately modelling this sort of multi-scale inactivation mechanism involving the collective motion of some $10^9$ atoms simultaneously with fatigue from atomic dislocations\cite{Physical2010} and reactive oxidation effects poses a significant computational and theoretical hassle, which has far exceeded our capabilities.

All-atom simulations of whole capsids are now possible, but existing pipelines tend to lack genome or nucleocapsid\cite{Mesoscale2020}\cite{Physical2017} and are extremely computationally demanding.

Coarse-graining is one route out; but, as with all abstractions in simulations, the problem must be set up with great care and experience (polarizable water; proper heat-bath damping coefficients and choice of integrator)\cite{Membrane2016}\cite{Determining2014}, and with an understanding of possible failure modes; we did not trust our abilities to produce correct results. An illustrative GROMACS simulation of a liposome, trajectories fourier transformed with \cite{TRAVIS2011}, was used to determine some parameters\footnote{implemented at \ghfile{/biology/simulation/GROMACS/BUMPy_bilayer/}, see supplemental}.

Parameterizing coarse bead-spring models based on all-atom simulations of small capsid segments or proteins \cite{Elucidating2009} is another technique. In this case, DNA/RNA can be represented by homogeneous beads restrained by Lennard-Jones forces \cite{Communication2013}. Mechanically reasonable coarse-grained models have recently been published for SARS-NCoV-2\cite{Multiscale2020}. Finite-element analysis \cite{Finite2008}

Coupling finite-element and Poisson-Boltzmann\cite{Electrostatic2020a}.

An approximate charge distribution of the proteins of the virion can be obtained by multiplying primary structure charges (in our case, extracted \cite{CIDER2017}, or (\cite{complete2003})) by observed protein contribution to total MW\cite{Quantitative1981}, old 2D-PAGE gels \cite{Influenza1978}\cite{Structurea} (which also provides an estimate of the variation in the charge, important for accurate spectroscopy, see supplemental) - or perhaps directly via extraction from whole-virion CryoEM maps, enabled by the charge-sensitive nature of the technique \cite{Identification2018}\cite{Electrostatic2020}. This has not yet been implemented in any software tools and seems quite tricky.

The genome charge is almost entirely neutralized by the nucleocapsid.

In our cursory testing, Bacteriophage T4 did not appear to be lysed by 10 microsecond pulses between 6 and 12 GHz at about $10^2$ to $10^3$ V/m, nor, exploring non-resonant inactivation, did nanosecond pulses up to a few MV/m appear to have any effect. Note that neither of these regimes overlap with the results of the previous studies.

@@

A rotational drag coefficient can extracted from MD simulation\cite{Evaluating2017}. We simulated a 30 nm lipid liposome using the MARTINI coarse-grained \cite{MARTINI2007}\cite{BUMPy2018}\cite{Tsjerk2020} lipid force fields with GROMACS\cite{GROMACS2005}' torque measurement feature, kindly implemented by Kutzner \cite{Keep2011}. This suggests a maximum rotation frequency on the order of $10^3$, but this value requires so many assumptions that it's hardly worth mentioning. From \cite{Spinning2008}, the upper bound of a homogenous spherical virus with 10 MPa overall tensile strength appears to be about $10^9$ Hz. \footnote{\ghfile{documents/optical_centrifuge.ipynb}}

@@

Dispersion and Brillouin precursors do offer a means to produce a significant improvement in loss through tissue, and the required electrical waveforms appear to be synthesizeable by variable-impedance or stub transmission-line pulse shaping\cite{Coaxial1985}\cite{Arbitrarya}.

@@

T4r was selected for biosafety reasons, and because of the large amount of structural data available. T4\cite{History1995} does not have a nucleocapsid; the charge distribution is likely much stronger than other RNA-like viruses Phi 6\footnote{Naming organisms with greek letters makes literature review somewhat more difficult, because many search engines do not support Unicode.}. Some more useful surrogates may include Pseudomonas Phi 6\cite{Selection2017}, the lipid-bearing PM2, PRD1 or PR4\cite{Lipidcontaining1979} if the outer protein capsid is dissolved\cite{Bacteriophage2002}, \cite{Dissociation1993}, or lipid liposomes. Certain phages also allow efficient concentration without ultracentrifuge, either by PEG precipitation\cite{Rapid1970} and settling, or via VIRADEL\cite{GROWTH}\cite{Chemical1982}\cite{highly1988}\cite{AdsorptionElution1989}, by altering the zeta potential of a syringe filter.

@@

When phage is rapidly immersed in solution of high osmotic strength, the active system that maintains osmotic equilibrium is overwhelmed, and the resulting pressure ruptures the capsid when it exceeds 100 atm \cite{Osmotic2003}. By $\sigma = pr / 2t $ t = 5.7 nm\cite{Head1988} and r=60 nm, capsid strength should be about 53 MPa, less than the 100 to 300 MPa cited by \cite{Bacteriophage2004}.
%((100 atm * 60 nanometers) / (2*(5.7 nanometers))) to MPa

\subsection{Experiment methods}

@@

E. coli produces the enzyme $\beta$-galactosidase to break lactose into glucose for later metabolism. A luciferase-based luminescent assay, Promega Beta-Glo, was evaluated, as described in\cite{rapid2014}. One component of the beta-glo contains a proprietary detergent designed to lyse cells\cite{BETAGLO2003} and expose the enzyme, counterproductive for phage use. Perhaps the detergent is not effective on bacteria, or the paper substrate that was used is sufficient. The detergent could perhaps be removed with BioBeads if this is desired.

While undoubtedly essential and very effective for its intended purpose (accurately quantifying lac operon activity), because of ambiguities in the rise and decay of the luminescence signal, short shelf life after the two components are mixed, oxygen depletion in small cuvettes, concerns regarding the detergent, and cost, Beta-Glo compared unfavorably to direct fluorescence or X-Gal for this specific application.

@@

@@
